\documentclass[../main.tex]{subfiles}

\makeatletter
\renewcommand{\xRightarrow}[2][]{\ext@arrow 0359\Rightarrowfill@{#1}{#2}}
\makeatother

\begin{document}

\subsection{Setup of \texorpdfstring{$\cSH$}{SH}}\label{setup}

In order to construct an abstract version of the Adams spectral sequence, we need to work in some axiomatic version of a stable homotopy category $\cSH$ which acts like the familiar classical stable homotopy category $\hoSp$ (\Cref{classical}) or the motivic stable homotopy category $\SH\scS$ over some base scheme $\scS$ (\Cref{motivic}). 

\begin{definition}\label{defn_compact}
	Let $\cC$ be an additive category with arbitrary (small) coproducts. Then an object $X$ in $\cC$ is \emph{compact} if, for any collection of objects $Y_i$ in $\cC$ indexed by some (small) set $I$, the canonical map
	\[\bigoplus_i\cC(X,Y_i)\to\cC(X,\bigoplus_iY_i)\]
	is an isomorphism of abelian groups. (Explicitly, the above map takes a generator $x\in\cC(X,Y_i)$ to the composition $X\xr xY_i\into\bigoplus_iY_i$.)
\end{definition}

\begin{definition}\label{sub_Picard_grading_defn}
	Given a tensor triangulated category $(\cC,\otimes,S,\Sigma,e,\cD)$ (\autoref{tentri}), a \emph{sub-Picard grading} on $\cC$ is the following data:
	\begin{itemize}
		\item A pointed abelian group $(A,\1)$ along with a homomorphism of pointed groups $h:(A,\1)\to(\Pic\cC,\Sigma S)$, where $\Pic\cC$ is the \emph{Picard group} of isomorphism classes of invertible objects in $\cC$.\footnote{Recall an object $X$ is a symmetric monoidal category is \emph{invertible} if there exists some object $Y$ and an isomorphism $S\cong X\otimes Y$.}
		\item For each $a\in A$, a chosen representative $S^a$ in the isomorphism class $h(a)$ such that each $S^a$ is a compact object (\autoref{defn_compact}) and $S^0=S$.
		\item For each $a,b\in A$, an isomorphism $\phi_{a,b}:S^{a+b}\to S^a\otimes S^b$. This family of isomorphisms is required to be \emph{coherent}, in the following sense:
		\begin{itemize}
			\item For all $a\in A$, we must have that $\phi_{a,0}$ coincides with the right unitor $S^{a}\xrightarrow\cong S^a\otimes S$ and $\phi_{0,a}$ coincides the left unitor $S^a\xrightarrow\cong S\otimes S^a$.
			\item For all $a,b,c\in A$, the following ``associativity diagram'' must commute:
			\[\begin{tikzcd}
				{S^{a+b}\otimes S^c} & {S^{a+b+c}} & {S^a\otimes S^{b+c}} \\
				{(S^a\otimes S^b)\otimes S^c} && {S^a\otimes(S^b\otimes S^c)}
				\arrow["{\phi_{a+b,c}}"', from=1-2, to=1-1]
				\arrow["{\phi_{a,b+c}}", from=1-2, to=1-3]
				\arrow["{S^a\otimes\phi_{b,c}}", from=1-3, to=2-3]
				\arrow["{\phi_{a,b}\otimes S^c}"', from=1-1, to=2-1]
				\arrow["\cong", from=2-1, to=2-3]
			\end{tikzcd}\]
		\end{itemize}
	\end{itemize}
\end{definition}

\begin{remark}\label{unique_comp_Sas}
	Note that by induction the coherence conditions for the $\phi_{a,b}$'s in the above definition say that given any $a_1,\ldots,a_n\in A$ and $b_1,\ldots,b_m\in A$ such that $a_1+\cdots+a_n=b_1+\cdots+b_m$ and any fixed parenthesizations of $X=S^{a_1}\otimes\cdots\otimes S^{a_b}$ and $Y=S^{b_1}\otimes\cdots\otimes S^{b_m}$, there is a \emph{unique} isomorphism $X\to Y$ that can be obtained by forming formal compositions of products of $\phi_{a,b}$, identities, associators, unitors, and their inverses (but not symmetries).
\end{remark}

From now on we fix a
monoidal closed tensor triangulated category $(\cSH,\otimes,S,\Sigma,e,\cD)$ with arbitrary (small) (co)products and sub-Picard grading $(A,\1,h,\{S^a\},\{\phi_{a,b}\})$. We also fix an isomorphism $\nu:\Sigma S\xr\cong S^\1$ once and for all.
We establish some conventions. First of all, given %objects $X_1,\ldots,X_n$ in $\cSH$, we write $X_1\otimes\cdots\otimes X_n$ to denote the object
%\[X_1\otimes(X_2\otimes\cdots(X_{n-1}\otimes X_n)).\]
%In particular, given 
an object $X$ and a natural number $n>0$, we write
\[X^n:=\overbrace{X\otimes\cdots\otimes X}^\text{$n$ times}\qquad\text{and}\qquad X^0:=S.\]
We denote the associator, symmetry, left unitor, and right unitor isomorphisms in $\cSH$ by
\[\begin{split}
	\alpha_{X,Y,Z}:(X\otimes Y)\otimes Z&\xrightarrow\cong X\otimes(Y\otimes Z) \\
	\lambda_X:S\otimes  X&\xrightarrow\cong X 
\end{split}\qquad\qquad\begin{split}
	\tau_{X,Y}:X\otimes Y &\xrightarrow\cong Y\otimes X\\
	\rho_X:X\otimes S&\xrightarrow\cong X.
\end{split}\]
Often we will drop the subscripts. Furthermore, by the coherence theorem for symmetric monoidal categories, we will often assume $\alpha$, $\rho$, and $\lambda$ are actual equalities. Given some integer $n\in\bZ$, we will write a bold $\n$ to denote the element $n\cdot\1$ in $A$. Note that we can use the isomorphism $\nu:\Sigma S\xr\cong S^\1$ to construct a natural isomorphism $\Sigma\cong S^\1\otimes-$:
\[\Sigma X\xr{\Sigma\lambda_X^{-1}}\Sigma(S\otimes X)\xr{e_{S,X}^{-1}}\Sigma S\otimes X\xr{\nu\otimes X}S^\1\otimes X.\]
The first two arrows are natural in $X$ by definition. The last arrow is natural in $X$ by functoriality of $-\otimes-$. By abuse of notation, we will also use $\nu$ to denote this natural isomorphism. \todo{is this characterization of $\nu$ and $e$ needed?}Furthermore, under this isomorphism, $e_{X,Y}:\Sigma X\otimes Y\xrightarrow\cong \Sigma(X\otimes Y)$ corresponds to the associator, by commutativity of the following diagram:
% https://q.uiver.app/#q=WzAsOSxbMywwLCIoU15cXDFcXG90aW1lcyBYKVxcb3RpbWVzIFkiXSxbMywyLCJTXlxcMVxcb3RpbWVzKFhcXG90aW1lcyBZKSJdLFsyLDAsIihcXFNpZ21hIFNcXG90aW1lcyBYKVxcb3RpbWVzIFkiXSxbMSwwLCJcXFNpZ21hKFNcXG90aW1lcyBYKVxcb3RpbWVzIFkiXSxbMCwwLCJcXFNpZ21hIFhcXG90aW1lcyBZIl0sWzAsMiwiXFxTaWdtYShYXFxvdGltZXMgWSkiXSxbMiwyLCJcXFNpZ21hIFNcXG90aW1lcyAoWFxcb3RpbWVzIFkpIl0sWzEsMiwiXFxTaWdtYShTXFxvdGltZXMgKFhcXG90aW1lcyBZKSkiXSxbMSwxLCJcXFNpZ21hKChTXFxvdGltZXMgWClcXG90aW1lcyBZKSJdLFswLDEsIlxcYWxwaGEiLDJdLFswLDIsIihcXG51XFxvdGltZXMgWClcXG90aW1lcyBZIiwyXSxbMywyLCJlX3tTLFh9XnstMX1cXG90aW1lcyBZIl0sWzQsMywiXFxTaWdtYVxcbGFtYmRhX1heey0xfVxcb3RpbWVzIFkiXSxbNCw1LCJlX3tYLFl9IiwyXSxbNiwxLCJcXG51XFxvdGltZXMgKFhcXG90aW1lcyBZKSIsMl0sWzcsNiwiZV97UyxYXFxvdGltZXMgWX1eey0xfSIsMl0sWzUsNywiXFxTaWdtYVxcbGFtYmRhX3tYXFxvdGltZXMgWX1eey0xfSIsMl0sWzIsNiwiXFxhbHBoYSJdLFszLDgsImVfe1NcXG90aW1lcyBYLFl9Il0sWzgsNywiXFxTaWdtYVxcYWxwaGEiXSxbOCw1LCJcXFNpZ21hKFxcbGFtYmRhX1hcXG90aW1lcyBZKSIsMV1d
\[\begin{tikzcd}
	{\Sigma X\otimes Y} & {\Sigma(S\otimes X)\otimes Y} & {(\Sigma S\otimes X)\otimes Y} & {(S^\1\otimes X)\otimes Y} \\
	& {\Sigma((S\otimes X)\otimes Y)} \\
	{\Sigma(X\otimes Y)} & {\Sigma(S\otimes (X\otimes Y))} & {\Sigma S\otimes (X\otimes Y)} & {S^\1\otimes(X\otimes Y)}
	\arrow["\alpha"', from=1-4, to=3-4]
	\arrow["{(\nu\otimes X)\otimes Y}"', from=1-4, to=1-3]
	\arrow["{e_{S,X}^{-1}\otimes Y}", from=1-2, to=1-3]
	\arrow["{\Sigma\lambda_X^{-1}\otimes Y}", from=1-1, to=1-2]
	\arrow["{e_{X,Y}}"', from=1-1, to=3-1]
	\arrow["{\nu\otimes (X\otimes Y)}"', from=3-3, to=3-4]
	\arrow["{e_{S,X\otimes Y}^{-1}}"', from=3-2, to=3-3]
	\arrow["{\Sigma\lambda_{X\otimes Y}^{-1}}"', from=3-1, to=3-2]
	\arrow["\alpha", from=1-3, to=3-3]
	\arrow["{e_{S\otimes X,Y}}", from=1-2, to=2-2]
	\arrow["\Sigma\alpha", from=2-2, to=3-2]
	\arrow["{\Sigma(\lambda_X\otimes Y)}"{description}, from=2-2, to=3-1]
\end{tikzcd}\]
Commutativity of the left trapezoid is naturality of $e$. The bottom left triangle commutes by coherence for monoidal categories and functoriality of $\Sigma$. Commutativity of the middle square is axiom TT4 for a tensor triangulated category. Finally, the right square commutes by naturality of $\alpha$.

Given some $a\in A$, we define $\Sigma^a:=S^a\otimes-$ and $\Omega^a:=\Sigma^{-a}=S^{-a}\otimes-$. We specifically define $\Omega:=\Omega^\1$. We say ``the $a^\text{th}$ suspension of $X$'' to denote $\Sigma^aX$. We will see later that for each $a\in A$, $\Sigma^a$ and $\Omega^a$ form an adjoint equivalence of $\cSH$ (\autoref{Sigma^a,Sigma^-a_adjoint_equiv_main}), so that in particular since $\Omega$ forms an adjoint equivalence with $\Sigma^\1\cong\Sigma$, $\cSH$ is canonically an \emph{adjointly} triangulated category (\autoref{adjointly_triangulated_defn}).

Given two objects $X$ and $Y$ in $\cSH$, we will denote the hom-abelian group of morphisms from $X$ to $Y$ in $\cSH$ by $[X,Y]$, and the internal hom object by $F(X,Y)$. We can extend the abelian group $[X,Y]$ into an $A$-graded abelian group ${[X,Y]}_*$ by defining ${[X,Y]}_a:=[S^a\otimes X,Y]$. Given an object $X$ in $\cSH$ and some $a\in A$, we can define the abelian group
\[\pi_a(X):=[S^a,X],\]
which we call the \emph{$a^\text{th}$ stable homotopy group of $X$}. We write $\pi_*(X)$ for the $A$-graded abelian group $\bigoplus_{a\in A}\pi_a(X)$, so that in particular we have a canonical isomorphism
\[\pi_*(X)=[S^*,X]\cong{[S,X]}_*.\]
Given some other object $E$, we can define the $A$-graded abelian groups $E_*(X)$ and $E^*(X)$ by the formulas
\[E_a(X):=\pi_a(E\otimes X)=[S^a,E\otimes X]\qquad\text{and}\qquad E^a(X):=[X,S^a\otimes E].\]
We refer to the functor $E_*(-)$ as the \emph{homology theory represented by $E$}, or just $E$-homology, and we refer to $E^*(-)$ as the \emph{cohomology theory represented by $E$}, or just $E$-cohomology. Finally, we state the following definition in $\cSH$:

\begin{definition}\label{cellular}
	Define the class of \emph{cellular} objects in $\cSH$ to be the smallest class of objects such that:
	\begin{enumerate}
		\item For all $a\in A$, $S^a$ is cellular.
		\item If we have a distinguished triangle
		\[X\to Y\to Z\to\Sigma X\]
		such that two of the three objects $X$, $Y$, and $Z$ are cellular, than the third object is also cellular.
		\item Given a collection of cellular objects $X_i$ indexed by some (small) set $I$, the object $\bigoplus_{i\in I} X_i$ is cellular (recall we have chosen $\cSH$ to have arbitrary coproducts).
	\end{enumerate}
\end{definition}

\subsection{Miscellaneous facts about \texorpdfstring{$\cSH$}{SH}}\todo{what do I call this subsection?}

\begin{proposition}\label{Sigma^a,Sigma^-a_adjoint_equiv_main}
	For each $a\in A$, the functors $\Sigma^a$ and $\Omega^a$ canonically form an adjoint equivalence of $\cSH$. In particular, $\Omega$ and $\Sigma\cong\Sigma^\1$ form an adjoint equivalence, so that $\cSH$ is an \emph{adjointly} tensor triangulated category (\autoref{adjointly_triangulated_defn}).
\end{proposition}
\begin{proof}
	See \autoref{Sigma^a,Sigma^-a_adjoint_equiv}.
\end{proof}

\begin{lemma}\label{cellular_closed_under_iso}
	Let $X$ and $Y$ be two isomorphic objects in $\cSH$. Then $X$ is cellular iff $Y$ is cellular.
\end{lemma}
\begin{proof}
	Assume we have an isomorphism $f:X\xr\cong Y$ and that $X$ is cellular. Then consider the following commutative diagram
	% https://q.uiver.app/#q=WzAsOCxbMCwwLCJYIl0sWzEsMCwiWSJdLFsyLDAsIjAiXSxbMywwLCJcXFNpZ21hIFgiXSxbMSwxLCJYIl0sWzAsMSwiWCJdLFsyLDEsIjAiXSxbMywxLCJcXFNpZ21hIFgiXSxbMCwxLCJmIl0sWzEsMl0sWzIsM10sWzEsNCwiZl57LTF9Il0sWzAsNSwiIiwyLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbNSw0LCIiLDIseyJsZXZlbCI6Miwic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dLFs0LDZdLFs2LDddLFszLDcsIiIsMSx7ImxldmVsIjoyLCJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJub25lIn19fV0sWzIsNiwiIiwxLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XV0=
	\[\begin{tikzcd}
		X & Y & 0 & {\Sigma X} \\
		X & X & 0 & {\Sigma X}
		\arrow["f", from=1-1, to=1-2]
		\arrow[from=1-2, to=1-3]
		\arrow[from=1-3, to=1-4]
		\arrow["{f^{-1}}", from=1-2, to=2-2]
		\arrow[Rightarrow, no head, from=1-1, to=2-1]
		\arrow[Rightarrow, no head, from=2-1, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow[from=2-3, to=2-4]
		\arrow[Rightarrow, no head, from=1-4, to=2-4]
		\arrow[Rightarrow, no head, from=1-3, to=2-3]
	\end{tikzcd}\]
	The bottom row is distinguished by axiom TR1 for a triangulated category. Hence since $X$ is cellular, $0$ is also cellular, since the class of cellular objects satisfies two-of-three for distinguished triangles. Furthermore, since the vertical arrows are all isomorphisms, the top row is distinguished as well, by axiom TR0. Thus again by two-of-three, since $X$ and $0$ are cellular, so is $Y$, as desired.
\end{proof}

\begin{lemma}\label{cellular_closed_under_tensor}
	Let $X$ and $Y$ be cellular objects in $\cSH$. Then $X\otimes Y$ is cellular.
\end{lemma}
\begin{proof}
	Let $E$ be a cellular object in $\cSH$, and let $\cE$ be the collection of objects $X$ in $\cSH$ such that $E\otimes X$ is cellular. First of all, suppose we have a distinguished triangle
	\[X\to Y\to Z\to\Sigma X\]
	such that two of three of $X$, $Y$, and $Z$ belong to $\cE$. Then since $\cSH$ is tensor triangulated, we have a distinguished triangle
	\[E\otimes X\to E\otimes Y\to E\otimes Z\to \Sigma(E\otimes X).\]
	Per our assumptions, two of three of $E\otimes X$, $E\otimes Y$, and $E\otimes Z$ are cellular, so that the third is by definition. Thus, all three of $X$, $Y$, and $Z$ belong to $\cE$ if two of them do.

	Second of all, suppose we have a family $X_i$ of objects in $\cE$ indexed by some (small) set $I$, and set $X:=\bigoplus_iX_i$. Then we'd like to show $X$ belongs to $\cE$, i.e., that $E\otimes X$ is cellular. Indeed,
	\[E\otimes X=E\otimes\(\bigoplus_iX_i\)\cong\bigoplus_i(E\otimes X_i),\]
	where the isomorphism is given by the fact that $\cSH$ is monoidal closed, so $E\otimes-$ preserves arbitrary colimits as it is a left adjoint. Per our assumption, since each $E\otimes X_i$ is cellular, the rightmost object is cellular, since the class of cellular objects is closed under taking arbitrary coproducts, by definition. Hence $E\otimes X$ is cellular by \autoref{cellular_closed_under_iso}.

	Finally, we would like to show that each $S^a$ belongs to $\cE$, i.e., that $S^a\otimes E$ is cellular for all $a\in A$. When $E=S^b$ for some $b\in A$, this is clearly true, since $S^b\otimes S^a\cong S^{a+b}$, which is cellular by definition, so that $S^b\otimes S^a$ is cellular by \autoref{cellular_closed_under_iso}. Thus by what we have shown, the class of objects $X$ for which $S^a\otimes X$ is cellular contains every cellular object. Hence in particular $E\otimes S^a\cong S^a\otimes E$ is cellular for all $a\in A$, as desired.
\end{proof}

\begin{lemma}\label{cellular_pi*=0_implies_contractible}
	Let $W$ be a cellular object in $\cSH$ such that $\pi_*(W)=0$. Then $W\cong 0$.
\end{lemma}
\begin{proof}
	Let $\cE$ be the collection of all $X$ in $\cSH$ such that $[\Sigma^nX,W]=0$ for all $n\in\bZ$ (where for $n>0$, $\Sigma^{-n}:=\Omega^n=(S^{-\1}\otimes-)^n$). We claim $\cE$ contains every cellular object in $\cSH$. First of all, each $S^a$ belongs to $\cE$, as 
	\[[\Sigma^nS^a,W]\cong[(\Sigma^\1)^nS^a,W]\cong[S^{a+\n},W]\leq\pi_*(W)=0.\] 
	Furthermore, suppose we are given a distinguished triangle
	\[X\to Y\to Z\to\Sigma X\]
	such that two of three of $X$, $Y$, and $Z$ belong to $\cE$. By \autoref{dist_tri_LES}, for all $n\in\bZ$ we get an exact sequence
	\[[\Sigma^{n+1}X,W]\to[\Sigma^nZ,W]\to[\Sigma^nY,W]\to[\Sigma^nX,W]\to[\Sigma^{n-1}Z,W].\]
	Clearly if any two of three of $X$, $Y$, and $Z$ belong to $\cE$, then by exactness of the above sequence all three of the middle terms will be zero, so that the third object will belong to $\cE$ as well. Finally, suppose we have a collection of objects $X_i$ in $\cE$ indexed by some small set $I$. Then
	\[\left[\Sigma^n\bigoplus_iX_i,W\right]\cong\left[\bigoplus_i\Sigma^nX_i,W\right]\cong\prod_i[\Sigma^nX_i,W]=\prod_i0=0,\]
	where the first isomorphism follows by the fact that $\Sigma^n$ is apart of an adjoint equivalence (\autoref{Sigma^a,Sigma^-a_adjoint_equiv_main}), so it preserves arbitrary colimits.

	Thus, by definition of cellularity, $\cE$ contains every cellular object. In particular, $\cE$ contains $W$, so that $[W,W]=0$, meaning in particular that $\id_W=0$, so we have a commutative diagram
	% https://q.uiver.app/#q=WzAsNCxbMCwxLCJXIl0sWzEsMCwiMCJdLFsyLDEsIlciXSxbMywwLCIwIl0sWzAsMV0sWzEsMl0sWzIsM10sWzEsMywiIiwwLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMCwyLCIiLDAseyJsZXZlbCI6Miwic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoibm9uZSJ9fX1dXQ==
	\[\begin{tikzcd}
		& 0 && 0 \\
		W && W
		\arrow[from=2-1, to=1-2]
		\arrow[from=1-2, to=2-3]
		\arrow[from=2-3, to=1-4]
		\arrow[Rightarrow, no head, from=1-2, to=1-4]
		\arrow[Rightarrow, no head, from=2-1, to=2-3]
	\end{tikzcd}\]
	Hence the diagonals exhibit isomorphisms between $0$ and $W$, as desired.
\end{proof}

\begin{theorem}\label{whitehead}
	Let $X$ and $Y$ be cellular objects in $\cSH$, and suppose $f:X\to Y$ is a morphism such that $f_*:\pi_*(X)\to\pi_*(Y)$ is an isomorphism. Then $f$ is an isomorphism.
\end{theorem}
\begin{proof}
	By axiom TR2 for a triangulated category (\autoref{triangulated_defn}), we have a distinguished triangle
	\[X\xr fY\xr gC_f\xr h\Sigma X.\]
	First of all, note that by definition since $X$ and $Y$ are cellular, so is $C_f$. Now, we claim $\pi_*(C_f)=0$. Indeed, given $a\in A$, by \autoref{dist_tri_LES} we have the following exact sequence:
	\[[S^a,X]\xr{f_*}[S^a,Y]\xr{g_*}[S^a,C_f]\xr{h_*}[S^a,\Sigma X]\xr{-(\Sigma f)_*}[S^a,\Sigma Y],\]
	where the first arrow is an isomorphism, per our assumption that $f_*$ is an isomorphism. To see the last arrow is an isomorphism, consider the following diagram:
	% https://q.uiver.app/#q=WzAsOCxbMCwwLCJbU15hLFxcU2lnbWEgWF0iXSxbMiwwLCJbU15hLFxcU2lnbWEgWV0iXSxbMCwxLCJbU15hLFNee1xcMX1cXG90aW1lcyBYXSJdLFsyLDEsIltTXmEsU15cXDFcXG90aW1lcyBZXSJdLFswLDIsIltTXnstXFwxfVxcb3RpbWVzIFNee2F9LFhdIl0sWzIsMiwiW1Neey1cXDF9XFxvdGltZXMgU157YX0sWV0iXSxbMCwzLCJbU157YS1cXDF9LFhdIl0sWzIsMywiW1Nee2EtXFwxfSxZXSJdLFswLDEsIihcXFNpZ21hIGYpXyoiXSxbMCwyLCIoXFxudV9YKV8qIiwyXSxbMSwzLCIoXFxudV9ZKV8qIl0sWzIsMywiKFNeXFwxXFxvdGltZXMgZilfKiJdLFs0LDUsImZfKiJdLFsyLDQsIlxcY29uZyIsMl0sWzMsNSwiXFxjb25nIl0sWzQsNiwieyhcXHBoaV97LVxcMSxhfSl9KiIsMl0sWzYsNywiZl8qIl0sWzUsNywieyhcXHBoaV97LVxcMSxhfSl9KiJdXQ==
	\[\begin{tikzcd}
		{[S^a,\Sigma X]} && {[S^a,\Sigma Y]} \\
		{[S^a,S^{\1}\otimes X]} && {[S^a,S^\1\otimes Y]} \\
		{[S^{-\1}\otimes S^{a},X]} && {[S^{-\1}\otimes S^{a},Y]} \\
		{[S^{a-\1},X]} && {[S^{a-\1},Y]}
		\arrow["{(\Sigma f)_*}", from=1-1, to=1-3]
		\arrow["{(\nu_X)_*}"', from=1-1, to=2-1]
		\arrow["{(\nu_Y)_*}", from=1-3, to=2-3]
		\arrow["{(S^\1\otimes f)_*}", from=2-1, to=2-3]
		\arrow["{f_*}", from=3-1, to=3-3]
		\arrow["\cong"', from=2-1, to=3-1]
		\arrow["\cong", from=2-3, to=3-3]
		\arrow["{{(\phi_{-\1,a})}*}"', from=3-1, to=4-1]
		\arrow["{f_*}", from=4-1, to=4-3]
		\arrow["{{(\phi_{-\1,a})}*}", from=3-3, to=4-3]
	\end{tikzcd}\]
	where the middle vertical arrows are the adjunction natural isomorphisms specified by \autoref{Sigma^a,Sigma^-a_adjoint_equiv_main}. The bottom arrow is an isomorphism per our assumptions, so the top arrow is likewise an isomorphism, as desired. Thus $\imm h_*=\ker -(\Sigma f)_*=0$, and $\ker g_*=\imm f_*=[S^a,Y]$, so that $\ker h_*=\imm g_*=0$. It is only possible that $\ker h_*=\imm h_*=0$ if $[S^a,C_f]=0$. Thus, we have shown $\pi_*(C_f)=0$, and $C_f$ is cellular, so by \autoref{cellular_pi*=0_implies_contractible} there is an isomorphism $C_f\cong 0$. Now consider the following commuting diagram:
	% https://q.uiver.app/#q=WzAsOCxbMCwwLCJYIl0sWzAsMSwiWSJdLFsxLDEsIlkiXSxbMSwwLCJZICJdLFsyLDEsIjAiXSxbMiwwLCJDX2YiXSxbMywwLCJcXFNpZ21hIFgiXSxbMywxLCJcXFNpZ21hIFkiXSxbMCwxLCJmIl0sWzEsMiwiIiwwLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMCwzLCJmIl0sWzMsMiwiIiwyLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XSxbMiw0XSxbMyw1XSxbNSw2XSxbNiw3LCJcXFNpZ21hIGYiXSxbNCw3XSxbNSw0LCJcXGNvbmciXV0=
	\[\begin{tikzcd}
		X & {Y } & {C_f} & {\Sigma X} \\
		Y & Y & 0 & {\Sigma Y}
		\arrow["f", from=1-1, to=2-1]
		\arrow[Rightarrow, no head, from=2-1, to=2-2]
		\arrow["f", from=1-1, to=1-2]
		\arrow[Rightarrow, no head, from=1-2, to=2-2]
		\arrow[from=2-2, to=2-3]
		\arrow[from=1-2, to=1-3]
		\arrow[from=1-3, to=1-4]
		\arrow["{\Sigma f}", from=1-4, to=2-4]
		\arrow[from=2-3, to=2-4]
		\arrow["\cong", from=1-3, to=2-3]
	\end{tikzcd}\]
	The top row is distinguished by assumption. The bottom row is distinguished by axiom TR2. Then since the middle two vertical arrows are isomorphisms, by \autoref{2-of-3-dist_tri-lemma}, $f$ is an isomorphism as well, as desired.
\end{proof}

\begin{proposition}\label{cellular_idempotent_splits_cellularly}
	Let $e:X\to X$ be an idempotent between cellular objects in $\cSH$, so by \autoref{idempotent_splits_in_tri_cat_with_countable_coproducts} there is a diagram
	\[X\xr rY\xr\iota X\]
	with $r\circ\iota=\id_Y$. Then $Y$ is cellular.
\end{proposition}
\begin{proof}
	It is a general categorical fact that an idempotent splits up to unique isomorphism, so by \autoref{cellular_closed_under_iso}, it suffices to show that $e$ has some cellular splitting. In \autoref{idempotent_splits_in_tri_cat_with_countable_coproducts}, it is shown that we may take $Y$ to be the homotopy colimit of the sequence
	\[X\xr eX\xr eX\xr eX\xr e\cdots,\]
	so there is a distinguished triangle
	\[\bigoplus_{i=0}^\infty X\to\bigoplus_{i=0}^\infty X\to Y\to\Sigma\(\bigoplus_{i=0}^\infty X\).\]
	Since $X$ is cellular, by definition $\bigoplus_{i=0}^\infty X$ is as well. Thus by 2-of-3 for distinguished triangles, $Y$ is cellular as desired.
\end{proof}

\begin{proposition}\label{X,Y*_LES}
	Suppose we are given a distinguished triangle
	\[X\xr fY\xr gZ\xr h\Sigma X\]
	and some object $W$ in $\cSH$. Then there is an infinite long exact sequence of $A$-graded abelian groups:
	\[\cdots\to{[W,Z]}_{*+\n+\1}\xr\partial{[W,X]}_{*+\n}\xr{f_*}{[W,Y]}_{*+\n}\xr{g_*}{[W,Z]}_{*+\n}\xr{\partial}{[W,Z]}_{*+\n-\1}\to\cdots,\]
	where $\partial:{[W,Z]}_{*+\n+\1}\to{[W,X]}_{*+\n}$ sends a class $x:S^{a+\n+\1}\otimes W\to Z$ to the composition 
	\[S^{a+\n}\otimes W\cong S^{-\1}\otimes S^{a+\n+\1}\otimes W\xrightarrow{S^{-\1}\otimes x}S^{-\1}\otimes Z\xrightarrow{S^{-\1}\otimes h}S^{-\1}\otimes \Sigma X\xrightarrow{S^{-\1}\otimes \nu_X}S^{-\1}\otimes S^\1\otimes X\xrightarrow{\phi_{-\1,\1}^{-\1}\otimes X}X.\]
\end{proposition}
\begin{proof}
	See \autoref{X,Y*_LES_appendix}.
\end{proof}

\begin{remark}\label{X,Y*_LES_compact}
	Expressed more compactly, the above proposition says that each object $W$ in $\cSH$ and distinguished triangle
	\[X\xr fY\xr gZ\xr h\Sigma X\]
	gives rise to the following diagram of $A$-graded abelian groups
	% https://q.uiver.app/#q=WzAsMyxbMCwwLCJ7W1csWF19XyoiXSxbMSwwLCJ7W1csWV19XyoiXSxbMSwxLCJ7W1csWl19XyoiXSxbMCwxLCJmXyoiXSxbMSwyLCJnXyoiXSxbMiwwLCJcXHBhcnRpYWwiXV0=
	\[\begin{tikzcd}
		{{[W,X]}_*} & {{[W,Y]}_*} \\
		& {{[W,Z]}_*}
		\arrow["{f_*}", from=1-1, to=1-2]
		\arrow["{g_*}", from=1-2, to=2-2]
		\arrow["\partial", from=2-2, to=1-1]
	\end{tikzcd}\]
	which is exact at each vertex, and where $f_*$, $g_*$, and $\partial$ are $A$-graded homomorphisms of degree $0$, $0$, and $-\1$, respectively. Explicitly, $\partial$ sends a class $x:S^a\otimes W\to Z$ to the composition
	\[S^{a-\1}\otimes W\cong S^{-\1}\otimes S^a\otimes W\xr{S^{-\1}\otimes x}S^{-\1}\otimes Z\xr{S^{-\1}\otimes h}S^{-\1}\otimes\Sigma X\xr{S^{-\1}\otimes\nu_X}S^{-\1}\otimes S^\1\otimes X\xr{\phi_{-\1,\1}^{-1}\otimes X}X.\]
\end{remark}

%Whether or not this happens is essentially the entire discussion of Dugger's paper \cite{Dugger_2014}, and as it turns out, $\pi_\ast(E)$ is in fact a graded ring provided we can choose these morphisms to be \emph{coherent}, in the following sense:
%
%\begin{theorem}[{\cite[Proposition 7.1]{Dugger_2014}}]\label{coherent_existence}
	%There exists a coherent family of isomorphisms
	%\[\phi_{a,b}:S^{a+b}\xrightarrow\cong S^a\otimes S^b\]
	%in the sense of \autoref{coherent_isos},
	%and in particular, the set of such coherent families is in bijective correspondence with the set of normalized $2$-cocycles $Z^2(A;\mathrm{Aut}(S))_\mathit{norm}$, i.e., the set of functions $\alpha:A\times A\to\mathrm{Aut}(S)$ such that $\alpha(0,0)=\id_S$ and for all $a,b,c\in A$, $\alpha(a+b,c)\cdot\alpha(a,b)=\alpha(b,c)\cdot\alpha(a,b+c)$. 
%\end{theorem}
%
%Thus, from now on we will suppose once and for all we have fixed a coherent family $\{\phi_{a,b}\}_{a,b\in A}$. Such a coherent family has very nice properties, in particular:

%Of course, we get our desired result: $\pi_*(E)$ is indeed an $A$-graded ring if $E$ is a monoid object.
%
%\begin{proposition}\label{pi_*E_is_ring_for_E_monoid}
	%Let $(E,\mu,e)$ be a commutative monoid object in $\cSH$, and consider the multiplication map $\pi_*(E)\times\pi_*(E)\to\pi_*(E)$ which sends classes $x:S^a\to E$ and $y:S^b\to E$ to the composition
	%\[S^{a+b}\xrightarrow{\phi_{a,b}}S^a\otimes S^b\xrightarrow{x\otimes y}E\otimes E\xrightarrow\mu E.\]
	%Then this endows $\pi_*(E)$ with the structure of an $A$-graded ring with unit $e\in\pi_0(E)=[S,E]$.
%\end{proposition}
%\begin{proof}
	%See \autoref{pi_*E_is_ring_for_E_monoid_appendix}. 
%\end{proof}
%
%Furthermore, it turns out that if $E$ is a \emph{commutative} monoid object in $\cSH$, then $\pi_\ast(E)$ is ``$A$-graded commutative,'' in the following sense:
%
%\begin{proposition}
	%For all $a,b\in A$ there exists an element $\theta_{a,b}\in\pi_0(S)=[S,S]$ (determined by choice of coherent family $\{\phi_{a,b}\}$) such that given any commutative monoid object $(E,\mu,e)$ in $\cSH$, the $A$-graded ring structure on $\pi_\ast(E)$ (\autoref{pi_*E_is_ring_for_E_monoid}) has a commutativity formula given by
	%\[x\cdot y=y\cdot x\cdot (e\circ\theta_{a,b})\]
	%for all $x\in\pi_a(E)$ and $y\in\pi_b(E)$.
%	
	%Furthermore, $\theta_{0,a}=\theta_{a,0}=\id_S$ for all $a\in A$, so that if either $x$ or $y$ has degree $0$, $x\cdot y=y\cdot x$.
%\end{proposition}
%\begin{proof}
	%See \autoref{pi_*(E)_is_A-graded_commutative_if_E_is_commutative} and \autoref{theta_a,0=theta_0,a=id_S}.
%\end{proof}
%
%The last ingredient in order to develop the Adams spectral sequence abstractly is a notion of \emph{cellularity} in $\cSH$:

\begin{proposition}
	Let $(E,\mu,e)$ be a monoid object in $\cSH$ (\autoref{monoid_object}). Then $\pi_*(E)$ is canonically an $A$-graded ring via the assignment $\pi_*(E)\times\pi_*(E)\to\pi_*(E)$ which takes classes $x:S^a\to E$ and $y:S^b\to E$ to the composition
	\[S^{a+b}\xr{\phi_{a,b}}S^a\otimes S^b\xr{x\otimes y}E\otimes E\xr\mu E.\]
	In particular, the unit for this ring is the element $e\in[S,E]=\pi_0(E)$.
\end{proposition}
\begin{proof}
	See \autoref{pi_*E_is_ring_for_E_monoid_appendix}.
\end{proof}

\begin{proposition}
	Let $(E,\mu,e)$ be a monoid object in $\cSH$. Then $E_*(-)$ is a functor from $\cSH$ to left $A$-graded $\pi_*(E)$-modules, where given some $X$ in $\cSH$, $E_*(X)$ may be endowed with the structure of a left $A$-graded $\pi_*(E)$-module via the map 
	\[\pi_*(E)\times E_*(X)\to E_*(X)\]
	which given $a,b\in A$, sends $x:S^a\to E$ and $y:S^b\to E\otimes X$ to the composition
	\[x\cdot y:S^{a+b}\cong S^a\otimes S^b\xrightarrow{x\otimes y}E\otimes (E\otimes X)\cong (E\otimes E)\otimes X\xrightarrow{\mu\otimes X}E\otimes X.\]
	Similarly, the assignment $X\mapsto X_*(E)$ is a functor from $\cSH$ to right $A$-graded $\pi_*(E)$-modules, where the structure map
	\[X_*(E)\times\pi_*(E)\to X_*(E)\]
	sends $x:S^a\to X\otimes E$ and $y:S^b\to E$ to the composition
	\[x\cdot y:S^{a+b}\cong S^a\otimes S^b\xrightarrow{x\otimes y}(X\otimes E)\otimes E\cong X\otimes(E\otimes E)\xrightarrow{X\otimes\mu}X\otimes E.\]
	Finally, $E_*(E)$ is a $\pi_*(E)$-bimodule, in the sense that the left and right actions of $\pi_*(E)$ are compatible, so that given $y, z\in\pi_*(E)$ and $x\in E_*(E)$, $y\cdot(x\cdot z)=(y\cdot x)\cdot z$.
\end{proposition}
\begin{proof}
	See \autoref{module}.
\end{proof}

\begin{lemma}\label{E_homology_suspension_iso_t^a's}
	Let $E$ and $X$ be objects in $\cSH$. Then for all $a\in A$, there is an $A$-graded isomorphism of $A$-graded abelian groups
	\[t^a_X:E_*(\Sigma^aX)\cong E_{*-a}(X)\]
	Furthermore this isomorphism is natural in $X$, and if $E$ is a monoid object in $\cSH$ then it is a natural isomorphism of left $\pi_*(E)$-modules.
\end{lemma}
\begin{proof}
	See \autoref{E_homology_suspension_iso_t^a's_appendix}.
\end{proof}

\begin{definition}\label{flat}
	Given a monoid object $E$ in $\cSH$, we say $E$ is \emph{flat} if the canonical right $\pi_*(E)$-module structure on $E_*(E)$ (see the above proposition) is that of a flat module.
\end{definition}

%\begin{proposition}
    %Suppose we have a distinguished triangle
    %\[X\xr fY\xr gZ\xr h\Sigma X\]
    %and an object $E$ in $\cSH$. Then there is an associated \emph{$E$-homology long exact sequence} of $A$-graded abelian groups:
    %% https://q.uiver.app/#q=WzAsOSxbMiwwLCJFX3sqK1xcbisxfShaKSJdLFswLDEsIkVfeyorXFxufShYKSJdLFsxLDEsIkVfeyorXFxufShZKSJdLFsyLDEsIkVfeyorXFxufShaKSJdLFswLDIsIkVfeyorXFxuLVxcMX0oWCkiXSxbMSwyLCJFX3sqK1xcbi1cXDF9KFkpIl0sWzEsMCwiRV97KitcXG4rXFwxfShZKSJdLFswLDAsIlxcY2RvdHMiXSxbMiwyLCJcXGNkb3RzIl0sWzAsMSwiXFxwYXJ0aWFsIiwxXSxbMSwyLCJFX3sqK1xcbn0oZikiLDJdLFsyLDMsIkVfeyorXFxufShnKSJdLFszLDQsIlxccGFydGlhbCIsMV0sWzQsNSwiRV97KitcXG4tXFwxfShmKSIsMl0sWzYsMCwiRV97KitcXG4rXFwxfShnKSJdLFs3LDZdLFs1LDhdXQ==
    %\[\begin{tikzcd}
        %\cdots & {E_{*+\n+\1}(Y)} & {E_{*+\n+1}(Z)} \\
        %{E_{*+\n}(X)} & {E_{*+\n}(Y)} & {E_{*+\n}(Z)} \\
        %{E_{*+\n-\1}(X)} & {E_{*+\n-\1}(Y)} & \cdots
        %\arrow["\partial"{description}, from=1-3, to=2-1]
        %\arrow["{E_{*+\n}(f)}"', from=2-1, to=2-2]
        %\arrow["{E_{*+\n}(g)}", from=2-2, to=2-3]
        %\arrow["\partial"{description}, from=2-3, to=3-1]
        %\arrow["{E_{*+\n-\1}(f)}"', from=3-1, to=3-2]
        %\arrow["{E_{*+\n+\1}(g)}", from=1-2, to=1-3]
        %\arrow[from=1-1, to=1-2]
        %\arrow[from=3-2, to=3-3]
    %\end{tikzcd}\]
    %extending infinitely in either direction, where $\partial:E_{*+\n+\1}(Z)\to E_{*+\n}(X)$ takes a class $x:S^{a+\n+\1}\to E\otimes Z$ to the composition
    %\[S^{a+\n}\cong S^{a+\n+\1}S^{-\1}\xr{x\otimes S^{-\1}} E\otimes Z\otimes S^{-\1}\xrightarrow{E\otimes h\otimes S^{-\1}}E\otimes S^\1\otimes X\otimes S^{-\1}\xr{E\otimes S^\1\otimes\tau}E\otimes S^\1\otimes S^{-\1}\otimes X\xr{E\otimes\phi_{\1,-\1}^{-1}\otimes X}E\otimes X\]
    %(where here we are ignoring associators and unitors).  Furthermore, if $(E,\mu,e)$ is a monoid object in $\cSH$, then the above sequence is a long exact sequence of left $A$-graded $\pi_*(E)$-modules.
%\end{proposition}
%\begin{proof}
	%First of all, note that by axiom TT3 for a tensor triangulated category, the following triangle is distinguished:
	%\[E\otimes X\xr{E\otimes f}E\otimes Y\xr{E\otimes g}E\otimes Z\xr{E\otimes'h} \Sigma(E\otimes X)\]
	%where $E\otimes' h$ is the composition
	%\[E\otimes Z\xr{E\otimes h}E\otimes\Sigma X\xr{e_{E,X}'}\Sigma(E\otimes X),\]
	%where $e'_{X,Y}:X\otimes\Sigma Y$ is the natural isomorphism given by the composition
	%\[X\otimes\Sigma Y\xr{\tau_{X,\Sigma Y}}\Sigma Y\otimes X\xr{e_{Y,X}}\Sigma(Y\otimes X)\xr{\Sigma\tau_{Y,X}}\Sigma(X\otimes Y).\]
	%(see \autoref{e'_defn}).
	%Since $\cSH$ is adjointly tensor triangulated (\autoref{Sigma^a,Sigma^-a_adjoint_equiv}), we can apply \autoref{dist_tri_LES} to this distinguished triangle to get a long exact sequence in $\cSH$, and applying $\pi_*=[S^*,-]$ yields the following long exact sequence of $A$-graded abelian groups:
    %% https://q.uiver.app/#q=WzAsMTksWzQsMCwiXFxwaV8qKFxcT21lZ2Fee24rMX0oRVxcb3RpbWVzIFopKSJdLFswLDIsIlxccGlfKihcXE9tZWdhXm4oRVxcb3RpbWVzIFgpKSJdLFsyLDIsIlxccGlfKihcXE9tZWdhXm4oRVxcb3RpbWVzIFkpKSJdLFs0LDIsIlxccGlfKihcXE9tZWdhXm4oRVxcb3RpbWVzIFopKSJdLFswLDQsIlxccGlfKihcXE9tZWdhXntuLTF9KEVcXG90aW1lcyBYKSkiXSxbMiw0LCJcXGNkb3RzIl0sWzIsMCwiXFxjZG90cyJdLFs0LDQsIlxccGlfKihcXE9tZWdhKEVcXG90aW1lcyBaKSkiXSxbMCw2LCJcXHBpXyooRVxcb3RpbWVzIFgpIl0sWzIsNiwiXFxwaV8qKEVcXG90aW1lcyBZKSJdLFs0LDYsIlxccGlfKihFXFxvdGltZXMgWikiXSxbMCw4LCJcXHBpXyooXFxTaWdtYShFXFxvdGltZXMgWCkpIl0sWzIsOCwiXFxjZG90cyJdLFs0LDgsIlxccGlfKihcXFNpZ21hXntuLTF9KEVcXG90aW1lcyBaKSkiXSxbMCwxMCwiXFxwaV8qKFxcU2lnbWFee259KEVcXG90aW1lcyBYKSkiXSxbMiwxMCwiXFxwaV8qKFxcU2lnbWFee259KEVcXG90aW1lcyBZKSkiXSxbNCwxMCwiXFxwaV8qKFxcU2lnbWFee259KEVcXG90aW1lcyBaKSkiXSxbMCwxMiwiXFxwaV8qKFxcU2lnbWFee24rMX0oRVxcb3RpbWVzIFgpKSJdLFsyLDEyLCJcXGNkb3RzIl0sWzAsMSwiXFxwaV8qKFxcT21lZ2FebihcXHdpZGV0aWxkZXtFXFxvdGltZXMnaH0pKSIsMV0sWzEsMiwiXFxwaV8qKFxcT21lZ2FebihFXFxvdGltZXMgZikpIiwyXSxbMiwzLCJcXHBpXyooXFxPbWVnYV5uKEVcXG90aW1lcyBnKSkiXSxbMyw0LCJcXHBpXyooXFxPbWVnYV57bi0xfShcXHdpZGV0aWxkZXtFXFxvdGltZXMnaH0pKSIsMV0sWzQsNV0sWzYsMF0sWzUsN10sWzcsOCwiXFxwaV8qKFxcd2lkZXRpbGRle0VcXG90aW1lcydofSkiLDFdLFs4LDksIlxccGlfKihFXFxvdGltZXMgZikiLDJdLFs5LDEwLCJcXHBpXyooRVxcb3RpbWVzIGcpIl0sWzEwLDExLCJcXHBpXyooRVxcb3RpbWVzJ2gpIiwxXSxbMTEsMTJdLFsxMiwxM10sWzEzLDE0LCJcXHBpXyooXFxTaWdtYV57bi0xfShFXFxvdGltZXMnaCkpIiwxXSxbMTQsMTUsIlxccGlfKihcXFNpZ21hXm4oRVxcb3RpbWVzIGYpKSIsMl0sWzE1LDE2LCJcXHBpXyooXFxTaWdtYV5uKEVcXG90aW1lcyBnKSkiXSxbMTYsMTcsIlxccGlfKihcXFNpZ21hXntufShFXFxvdGltZXMnaCkpIiwxXSxbMTcsMThdXQ==
    %\begin{equation}\label{E_LES_diag_1}\begin{tikzcd}
        %&& \cdots && {\pi_*(\Omega^{n+1}(E\otimes Z))} \\
        %\\
        %{\pi_*(\Omega^n(E\otimes X))} && {\pi_*(\Omega^n(E\otimes Y))} && {\pi_*(\Omega^n(E\otimes Z))} \\
        %\\
        %{\pi_*(\Omega^{n-1}(E\otimes X))} && \cdots && {\pi_*(\Omega(E\otimes Z))} \\
        %\\
        %{\pi_*(E\otimes X)} && {\pi_*(E\otimes Y)} && {\pi_*(E\otimes Z)} \\
        %\\
        %{\pi_*(\Sigma(E\otimes X))} && \cdots && {\pi_*(\Sigma^{n-1}(E\otimes Z))} \\
        %\\
        %{\pi_*(\Sigma^{n}(E\otimes X))} && {\pi_*(\Sigma^{n}(E\otimes Y))} && {\pi_*(\Sigma^{n}(E\otimes Z))} \\
        %\\
        %{\pi_*(\Sigma^{n+1}(E\otimes X))} && \cdots
        %\arrow["{\pi_*(\Omega^n(\widetilde{E\otimes'h}))}"{description}, from=1-5, to=3-1]
        %\arrow["{\pi_*(\Omega^n(E\otimes f))}"', from=3-1, to=3-3]
        %\arrow["{\pi_*(\Omega^n(E\otimes g))}", from=3-3, to=3-5]
        %\arrow["{\pi_*(\Omega^{n-1}(\widetilde{E\otimes'h}))}"{description}, from=3-5, to=5-1]
        %\arrow[from=5-1, to=5-3]
        %\arrow[from=1-3, to=1-5]
        %\arrow[from=5-3, to=5-5]
        %\arrow["{\pi_*(\widetilde{E\otimes'h})}"{description}, from=5-5, to=7-1]
        %\arrow["{\pi_*(E\otimes f)}"', from=7-1, to=7-3]
        %\arrow["{\pi_*(E\otimes g)}", from=7-3, to=7-5]
        %\arrow["{\pi_*(E\otimes'h)}"{description}, from=7-5, to=9-1]
        %\arrow[from=9-1, to=9-3]
        %\arrow[from=9-3, to=9-5]
        %\arrow["{\pi_*(\Sigma^{n-1}(E\otimes'h))}"{description}, from=9-5, to=11-1]
        %\arrow["{\pi_*(\Sigma^n(E\otimes f))}"', from=11-1, to=11-3]
        %\arrow["{\pi_*(\Sigma^n(E\otimes g))}", from=11-3, to=11-5]
        %\arrow["{\pi_*(\Sigma^{n}(E\otimes'h))}"{description}, from=11-5, to=13-1]
        %\arrow[from=13-1, to=13-3]
    %\end{tikzcd}\end{equation}
    %where $\wt{E\otimes'h}:\Omega(E\otimes Z)\to E\otimes X$ is the left adjoint of $E\otimes'h:E\otimes Z\to\Sigma(E\otimes X)$ (note here $\Sigma^n$ and $\Omega^n$ denote $n$ applications of $\Sigma=\Sigma^\1$ and $\Omega=\Omega^\1$, respectively. They are not the same as $\Sigma^\n$ or $\Omega^\n$). Note that for all $a\in A$ and $X$ in $\cSH$, we have an isomorphism $s_X^{a,n}:\pi_*((\Sigma^a)^nX)\cong\pi_{*-n\cdot a}(X)$ given by the composition
    %\[[S^*,\overbrace{S^a\otimes\cdots\otimes S^a}^\text{$n$ times}\otimes X]\xrightarrow{(\phi\otimes X)_*}[S^*,S^{n\cdot a}\otimes X]\cong[S^{-n\cdot a}\otimes S^*,X]\xrightarrow{(\phi_{-n\cdot a,*})^*}[S^{*-n\cdot a},X],\]
    %where the $\phi$ in the first arrow stands for the unique isomorphism $(S^a)^n\cong S^{n\cdot a}$ that can be obtained by composing copies of products of $\phi_{a,b}$'s, associators, unitors, and their inverses, and the middle isomorphism is the adjunction given by \autoref{Sigma^a,Sigma^-a_adjoint_equiv}. It is straightforward to see that each of the above arrows is natural in $X$ (the first is natural by functoriality of $-\otimes-$, the middle is natural as it is the isomorphism given by an adjunction, and the last is clearly natural simply by unravelling definitions). Thus for all $n>0$ we have isomorphisms of exact sequences
    %% https://q.uiver.app/#q=WzAsMTMsWzAsMCwiXFxwaV8qKFxcT21lZ2FebihFXFxvdGltZXMgWCkpIl0sWzEsMCwiXFxwaV8qKFxcT21lZ2FebihFXFxvdGltZXMgWSkpIl0sWzIsMCwiXFxwaV8qKFxcT21lZ2FebihFXFxvdGltZXMgWikpIl0sWzAsMSwiRV97KitcXG59KFgpIl0sWzEsMSwiRV97KitcXG59KFkpIl0sWzIsMSwiRV97KitcXG59KFopIl0sWzEsMiwiXFx0ZXh0e2FuZH0iXSxbMCwzLCJcXHBpXyooXFxTaWdtYV5uKEVcXG90aW1lcyBYKSkiXSxbMSwzLCJcXHBpXyooXFxTaWdtYV5uKEVcXG90aW1lcyBZKSkiXSxbMiwzLCJcXHBpXyooXFxTaWdtYV5uKEVcXG90aW1lcyBaKSkiXSxbMCw0LCJFX3sqLVxcbn0oWCkiXSxbMSw0LCJFX3sqLVxcbn0oWSkiXSxbMiw0LCJFX3sqLVxcbn0oWikiXSxbMCwxLCJcXHBpXyooXFxPbWVnYV5uKEVcXG90aW1lcyBmKSkiXSxbMSwyLCJcXHBpXyooXFxPbWVnYV5uKEVcXG90aW1lcyBnKSkiXSxbMCwzLCJzXnstXFwxLG59IiwyXSxbMyw0LCJFX3srXFxufShmKSIsMl0sWzQsNSwiRV97KitcXG59KGcpIiwyXSxbMSw0LCJzXnstXFwxLG59IiwyXSxbMiw1LCJzXnstXFwxLG59IiwyXSxbNyw4LCJcXHBpXyooXFxTaWdtYV5uKEVcXG90aW1lcyBmKSkiXSxbOCw5LCJcXHBpXyooXFxTaWdtYV5uKEVcXG90aW1lcyBnKSkiXSxbNywxMCwic157XFwxLG59IiwyXSxbMTAsMTEsIkVfeyotXFxufShmKSIsMl0sWzExLDEyLCJFX3sqLVxcbn0oZykiLDJdLFs4LDExLCJzXntcXDEsbn0iLDJdLFs5LDEyLCJzXntcXDEsbn0iLDJdXQ==
    %\[\begin{tikzcd}
        %{\pi_*(\Omega^n(E\otimes X))} & {\pi_*(\Omega^n(E\otimes Y))} & {\pi_*(\Omega^n(E\otimes Z))} \\
        %{E_{*+\n}(X)} & {E_{*+\n}(Y)} & {E_{*+\n}(Z)} \\
        %& {\text{and}} \\
        %{\pi_*(\Sigma^n(E\otimes X))} & {\pi_*(\Sigma^n(E\otimes Y))} & {\pi_*(\Sigma^n(E\otimes Z))} \\
        %{E_{*-\n}(X)} & {E_{*-\n}(Y)} & {E_{*-\n}(Z)}
        %\arrow["{\pi_*(\Omega^n(E\otimes f))}", from=1-1, to=1-2]
        %\arrow["{\pi_*(\Omega^n(E\otimes g))}", from=1-2, to=1-3]
        %\arrow["{s^{-\1,n}}"', from=1-1, to=2-1]
        %\arrow["{E_{+\n}(f)}"', from=2-1, to=2-2]
        %\arrow["{E_{*+\n}(g)}"', from=2-2, to=2-3]
        %\arrow["{s^{-\1,n}}"', from=1-2, to=2-2]
        %\arrow["{s^{-\1,n}}"', from=1-3, to=2-3]
        %\arrow["{\pi_*(\Sigma^n(E\otimes f))}", from=4-1, to=4-2]
        %\arrow["{\pi_*(\Sigma^n(E\otimes g))}", from=4-2, to=4-3]
        %\arrow["{s^{\1,n}}"', from=4-1, to=5-1]
        %\arrow["{E_{*-\n}(f)}"', from=5-1, to=5-2]
        %\arrow["{E_{*-\n}(g)}"', from=5-2, to=5-3]
        %\arrow["{s^{\1,n}}"', from=4-2, to=5-2]
        %\arrow["{s^{\1,n}}"', from=4-3, to=5-3]
    %\end{tikzcd}\]
    %It remains to show that the following diagram commutes:
%\end{proof}

\end{document}
